---
title: "Exercise 3"
author: "Dara Alifa (12246777), Constantin Schuh (12245505)"
date: "`r Sys.Date()`"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2023"
output:
 distill::distill_article: default
 bookdown::html_document2:
    number_sections: no
    df_print: paged
 html_document:
    number_sections: no
    df_print: paged
 pdf_document:
    number_sections: no
    df_print: paged
---

## Exercise 1

# d)

**Strengths of Git:**

1.  Distributed Version Control: Git's distributed nature allows for multiple copies of a repository to exist, which means developers can work offline and have their own local copy of the entire project history. This decentralization provides flexibility and resilience, as each developer has a complete backup of the codebase and can easily switch between branches.

2.  Powerful Branching and Merging: Git excels at branching and merging workflows, enabling developers to create and switch between branches to work on different features or bug fixes independently. The branching model in Git is lightweight and efficient, allowing for rapid iteration and experimentation. Merging branches is also straightforward, enabling smooth collaboration and integration of changes.

**Weaknesses of Git:**

1.  Steep Learning Curve: Git has a reputation for having a steep learning curve, especially for beginners. Its command-line interface and numerous features can be overwhelming initially. Concepts like branching, merging, rebasing, and resolving conflicts require understanding to use Git effectively. However, there are user-friendly graphical interfaces and tutorials available to ease the learning process.

2.  Complex Conflict Resolution: When multiple developers make conflicting changes to the same file or code segment, Git requires manual intervention to resolve the conflicts. Although Git provides tools to assist in resolving conflicts, it can still be a challenging and time-consuming process, particularly for larger projects with numerous contributors. Skill and careful attention are necessary to ensure conflicts are resolved correctly without introducing errors.

## Exercise 3

# a)

```{r}
vornamen_2021 <- read.csv("C:/Users/Const/Desktop/Bachelor Geographie/6. Semester/Fortgeschrittene Statistische Software/data/vornamen_2021.csv")
vornamen_2022 <- read.csv("C:/Users/Const/Desktop/Bachelor Geographie/6. Semester/Fortgeschrittene Statistische Software/data/open_data_portal_2022.csv")
typeof(vornamen_2021$Anzahl)
vornamen_2021$Anzahl <- as.numeric(vornamen_2021$Anzahl)
vornamen_2022$Anzahl <- as.numeric(vornamen_2022$Anzahl)
vornamen_2021[is.na(vornamen_2021)] <- 0
vornamen_2022[is.na(vornamen_2022)] <- 0
typeof(vornamen_2021$Anzahl)
typeof(vornamen_2022$Anzahl)
```

 * The Problem was that in "Anzahl" every Number under 5 was displayed as "4 oder weniger" which has characters. When you convert to numerical all rows with "4 oder weniger" turn into NA -> Missing values. To get rid of the missing values you turn them into 0.

# c)

```{r}
total_babies_2021 <- sum(vornamen_2021$Anzahl)
total_babies_2021
total_babies_2022 <- sum(vornamen_2022$Anzahl)
total_babies_2022
```

 * In 2021 was the bigger baby boom with 11524 babies. In 2022 only 9899 babies were born.
 
# d)

```{r}
vornamen_2021$year <- 2021
vornamen_2022$year <- 2022
```

# e)

```{r}
library(dplyr)
vornamen_2021_2022 <- dplyr::bind_rows(vornamen_2021, vornamen_2022)
```

# f)

```{r}
name_counts <- vornamen_2021_2022 %>%
  group_by(Vorname) %>%
  summarize(Total_Count = sum(Anzahl)) %>%
  arrange(desc(Total_Count))

top_10_names <- head(name_counts, 10)
knitr::kable(top_10_names, caption = "Top 10 Most Popular Names")
```




